### 2014-04-17 brains-garbage.tex
Acknowledge some changes, set comments for later

>>>>

\begin{figure*}[!th]
    \centering
    \includegraphics[width=0.95\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_no-exclusion.png}
    \caption{Recursive, minimum 20 timebags for each cluster, \textbf{previous quotes not excluded}}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=0.95\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_prevtbg-exclusion.png}
    \caption{Chains, minimum 20 timebags for each cluster, \textbf{excluding quotes from preceding timebag}}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=0.95\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_prevnew-exclusion.png}
    \caption{Chains, minimum 20 timebags for each cluster, \textbf{excluding quotes considered new in previous timebag}}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=0.95\textwidth]{images/computed-figures/timebags_evolution_recursive_shifting_min20_prevtbg-exclusion.png}
    \caption{Chains, \textbf{shifting clusters}, minimum 20 timebags for each cluster, \textbf{excluding quotes from preceding timebag}}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=0.95\textwidth]{images/computed-figures/timebags_evolution_recursive_shifting_min10_prevtbg-exclusion.png}
    \caption{Chains, \textbf{shifting clusters}, \textbf{minimum 10 timebags} for each cluster, \textbf{excluding quotes from preceding timebag}}
    \label{fig:timebags-evolution}
\end{figure*}

### 2014-04-17 brains-protocol.tex
Acknowledge some changes, set comments for later

We build two main observables for each word feature.
First, we measure the susceptibility for words to be the source of a substitution, knowing that there has been a variation, in order to show which semantic features are the most likely to attract a substitution \new{under this condition}.
Second, we measure the variation of word feature over a substitution, looking at the variation of a given feature between start and arrival words.

@@

For a given feature $\phi$, the protocol lets us compute substitution \emph{susceptibilities} for each feature value $f$.
We say that a word is \emph{substitutable} if it appears in a quote which undergoes a substitution, whether that substitution operates on the considered word or on another.
\rk{We also restrict to words substituted at least once.}
Word substitution susceptibility is computed as the ratio of the number $s_w$ of times a word is substituted to the number $p_w$ of times that word appears in a substitutable position, i.e. $\sfrac{s_w}{p_w}$.

Now averaging over all words such that $\phi(w) = f$, we obtain the mean susceptibility for the feature value $f$:
\footnote{To avoid any auto-correlation effect due to the number of substitutions in a cluster (possibly leading to an overly optimistic estimation of confidence intervals), we first average substitutions over each cluster, by considering the average of arrival word features for a given start word.
Indeed, substitutions occurring in the same cluster are likely not statistically independent.}
$$\sigma_{\phi}(f) \defeq \left< \frac{s_w}{p_w} \right>_{\left\lbrace w | \phi(w) = f \right\rbrace}$$

@@

>>>>

We build two main observables for each word feature.
First, we measure the susceptibility for words to be the source of a substitution, knowing that there has been a variation, in order to show which semantic features are the most likely to attract a substitution under this condition.
Second, we measure the variation of word feature over a substitution, looking at the variation of a given feature between start and arrival words.

@@

For a given feature $\phi$, the protocol lets us compute substitution \emph{susceptibilities} for each feature value $f$.
We say that a word is \emph{substitutable} if it appears in a quote which undergoes a substitution, whether that substitution operates on the considered word or on another.
Word substitution susceptibility is computed as the ratio of the number $s_w$ of times a word is substituted to the number $p_w$ of times that word appears in a substitutable position, i.e. $\sfrac{s_w}{p_w}$.

Now averaging over all words such that $\phi(w) = f$ (only taking into account words that are substituted at least once), we obtain the mean susceptibility for the feature value $f$:
\footnote{To avoid any auto-correlation effect due to the number of substitutions in a cluster (possibly leading to an overly optimistic estimation of confidence intervals), we first average substitutions over each cluster, by considering the average of arrival word features for a given start word.
Indeed, substitutions occurring in the same cluster are likely not statistically independent.}
$$\sigma_{\phi}(f) \defeq \left< \frac{s_w}{p_w} \right>_{\left\lbrace w | \phi(w) = f \right\rbrace}$$

@@

\subsection{Results}

\rk{Comment results}
